Multiproduct Batch Processing Time Maximization Problem

### 2023-06-17 (2023) Fraga et al.tex
updating paper
solving method :)
updating paper
including solution of exemple presented in section 2

\section{Multiproduct batch processing time maximization problem}
\label{}

@@

$T$ is the batch processing time.

@@

So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.

>>>>

\section{Multiproduct batch processing time maximization problem}
\label{sec:MBPTMP}

@@

$T$ is the batch processing time. \\

@@

So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value. \\

So the solution method can be decomposed into 4 steps: \\

step 1: find $T'$, where:

\begin{equation}
T' = \min {\textrm{UD}_i / \textrm{p}_i}
\end{equation}

step 2: calculate $S_i$ for all products. \\

step 3: find $T''$, where:

\begin{equation}
T'' = \min \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i, (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
\end{equation}

step 4: calculate $T$, where:

\begin{equation}
T = \min {T , Z}
\end{equation}

It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\

\emph{Solution for the example presented before} \\

Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\

$T' \leq 1000g / 60g/min$ \\

$T' \leq 16,67 min$ \quad for A \\

$T' \leq 500g / 40g/min$ \\

$T' \leq 12,50 min$ \quad for B \\

so: \\

$T' = 12$ \\

Then:\\

$S_A = 1000g - 12min * 60g/min = 280g$ \\

$S_B = 500g - 12min * 40g/min = 20g$ \\

And so we have: \\

$T'' \leq (3000g + 600g + 280g) / 60g/min$ \\

$T'' \leq 64,67 min$ \quad for A \\

$T'' \leq (2000g + 600g + 20g) / 40g/min$ \\

$T'' \leq 65,50 min$ \quad for B \\

$T'' \leq (1000g + 3000g + 300g) / 100g/min$ \\

$T'' \leq 43 min$ \quad for A and B \\

So that: \\

$T'' = 43 min$ \\

So we have: \\

$ T = 55 min$ \\

As $T<\textrm{Z}$, then this will certainly be the optimal solution. \\

In this case we will have: \\

$P_A = 3300g$ e $P_B=2200g$ \\

$D_A = 1000g$ e $D_B = 500g$ \\

$E_A = 2300g$ e $E_B = 1700g$ \\

Note that it is not important to know the values of $O_i$ and $I_i$ however these values can be found by solving the indeterminate system of equations:
